---
title: "Filtering and segmenting roads"
author: "Robin Lovelace"
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

```{r}
library(sp)
library(tmap)
library(rgeos)
library(geojsonio)
```

## Context

This project is motivated by a plan to create an online tool for crowdsoucing information about the cycle network. The policy problem it seeks to solve is that:

> Every city has a set of streets which could form a key cycle network.
Such a network would form the basis of investment priorities by
Local Authorities to make cycling easier and safer. Yet it is currently
hard for local people to express the extent and form of this network
in a coherent, consensus-driven way (CycleStreets.net, 2016).

## The problem

The problem with a crowd-sourced system is that everyone wants to comment everywhere.
This diversity is healthy but can make it hard to prioritise issues.
Also for newcomers to cycle campaigning the complexity of options can be confusing.

So there is a need for a simpler unit of analysis linked to the transport network.
This repository explores the creation of such a level of data: the segment.

## The data problem

Here we illustrate the problem with reference to data from Ordance Survey and OpenStreetMap:

```{r cars}
open_a_lds = geojson_read("data/open_a_lds.geojson", what = "sp")
qtm(open_a_lds) +
  tm_scale_bar()
summary(open_a_lds$length)
```

There is a wide range of distances in there. Most segments won't be of a size/shape of interest to people wanting to improve the road network. 
OSM data is also highly diverse in terms of lengths:

```{r}
osm_highways_lds = geojson_read("data/highways-osm-leeds.geojson", what = "sp")
qtm(osm_highways_lds) +
  tm_scale_bar()
summary(gLength(osm_highways_lds, byid = T))
```


